msc dissertation

### 2021-07-19 msc dissertation code.Rmd
Add files via upload

```
## reproduction of results (interaction between headline veracity and treatment)
### without considering attention check
```{r, message=FALSE}

lm1 = lm(Discern ~ condition, data = pennystudy2r1)
summary(lm1)

>>>>

#create veracity column (Real - Fake)
pennystudy2r1['veracity']=pennystudy2r1['Real'] - pennystudy2r1['Fake']

#successful screen1 test (result = 2)
pennystudy2r1['screen1']=pennystudy2r1['screen1_4'] + pennystudy2r1['screen1_7']

#successful screen2 test (result = 2)
pennystudy2r1['screen2']=pennystudy2r1['screen2_3'] + pennystudy2r1['screen2_5']

#successful screen3 test (result = 3)
pennystudy2r1['screen3'] = na_if(pennystudy2r1$screen3_2,1)
pennystudy2r1['screen3'] = na_if(pennystudy2r1$screen3,2)
pennystudy2r1['screen3'] = na_if(pennystudy2r1$screen3,4)
pennystudy2r1['screen3'] = na_if(pennystudy2r1$screen3,5)
#to check if screen 3 successful
mean(pennystudy2r1$screen3, na.rm = TRUE)

#replace 2 and 3 to 1
pennystudy2r1["screen1"][pennystudy2r1["screen1"] == 2] <- 1
pennystudy2r1["screen2"][pennystudy2r1["screen2"] == 2] <- 1
pennystudy2r1["screen3"][pennystudy2r1["screen3"] == 3] <- 1

## reproduction of results (interaction between headline veracity and treatment)
### without considering attention check
```{r, message=FALSE}
install.packages("sandwich") 
install.packages("stargazer")
install.packages("lmtest")
library(lmtest)
library(stargazer) 
library(sandwich)

lm1 <- lm(Discern ~ condition + veracity + veracity*condition, data = pennystudy2r1)
summary(lm1)

stargazer(lm1, type='text')

coeftest(lm1, vcovHC)

#z scored
scale(pennystudy2r1$Discern)

lm1 = lm(scale(pennystudy2r1$Discern) ~ condition, data = pennystudy2r1)
summary(lm1)
